Re-fit

### 2023-01-16 scripts/r/04_refit/refit_tr.Rmd
🐛 - fix wrong name of predictor in pseudopleuronectes_assasi_2_f0_cat

pseudopleuronectes_assasi_2_f0_cat <- brm(
  MedianST ~ 
         effect_cat + Sex +
         (1|Speaker) + 
         (1|TargetColor),
  seed = 111,
  data = NF1, 
  cores = 4,  
  file = "./data/analyses/models/pseudopleuronectes_assasi_2_f0_cat"
  )

>>>>

pseudopleuronectes_assasi_2_f0_cat <- brm(
  MedianST ~ 
         effect_cat + sex_s +
         (1|Speaker) + 
         (1|TargetColor),
  seed = 111,
  data = NF1, 
  cores = 4,  
  file = "./data/analyses/models/pseudopleuronectes_assasi_2_f0_cat"
  )
